---
title: "A3 - MAPPING"
author: "Janavi Moncourt"
date: "`r Sys.Date()`"
output: 
  html_document:
          theme: flatly
          toc: TRUE
          toc_float: TRUE
          toc_depth: 2
          number_sections: FALSE
          df_print: paged
          code_folding: show
          code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(rnaturalearth)
library(rnaturalearthdata)
library(tidyverse) 
library(tmap) 
library(osmplotr) 
library(leaflet) 
library(threejs) 
library(sf)
```

## **PART A** 

### **In part A of this project, we will be plotting all restaurants across Richmond Town, Bangalore**

### **Creating the bounding boxes** 

```{r}
bbox_1 <- osmplotr::get_bbox(latlon = c(77.46,12.83,77.74,13.14))
bbox_1
```

```{r}
bbox_2 <- osmdata::getbb("Richmond town, Bangalore, India")
bbox_2
```

### **Examining the bounding boxes**

```{r}
bbox_1
bbox_2
```

### **Downloading Data from Open Street Map**

```{r, eval=FALSE}
dat_buildings <-extract_osm_objects (key = "building", 
                                     bbox = bbox_2)
dat_roads <- extract_osm_objects (key = 'highway', 
                                     value = c("residential"),
                                     bbox = bbox_2)
dat_parks <- extract_osm_objects (key = 'park', 
                                  bbox = bbox_2)
dat_greenery <- extract_osm_objects (key = 'landuse', 
                                  value = 'grass', 
                                  bbox = bbox_2)
dat_trees <- extract_osm_objects (key = 'natural', 
                                  value = 'tree', 
                                  bbox = bbox_2)
dat_R <- extract_osm_objects(bbox = bbox_2, 
                             key = "amenity", 
                             value = "restaurant", 
                             return_type = "point")
```

### **Saving the data**

```{r,eval=FALSE}
st_write(dat_buildings, dsn = "./Data//buildings.gpkg", append = FALSE, 
         quiet = FALSE)
st_write(dat_parks, dsn = "./Data/parks.gpkg", append = FALSE, quiet = FALSE)
st_write(dat_greenery, dsn = "./Data//greenery.gpkg", append = FALSE,quiet = FALSE)
st_write(dat_trees, dsn = "./Data//trees.gpkg", append = FALSE,quiet = FALSE)

st_write(dat_roads, dsn = "./Data//roads.gpkg", append = FALSE, quiet = FALSE)
st_write(dat_R, dsn = "./Data//restaurants.gpkg", append = FALSE,quiet = FALSE)
```

### **Reading Back the saved Data**

```{r}
buildings <- st_read(dsn = "Data//buildings.gpkg")
parks <- st_read("Data/parks.gpkg")
greenery <- st_read("data/greenery.gpkg")
trees <- st_read("Data//trees.gpkg")
roads <- st_read("Data//roads.gpkg")
restaurants <- st_read("Data//restaurants.gpkg")
```
### **Cleaning up the restaurant data set in order to plot our mapping graphs** 

```{r}
restaurants$cuisine %>% unique()
```

```{r}
restaurants <- restaurants %>% 
  drop_na(cuisine) %>% 
  separate(col = cuisine, into = c("cuisine", NA, NA), sep = ";") %>% 
  separate(col = cuisine, into = c("cuisine", NA, NA), sep = ",")
```

```{r}
restaurants$cuisine
```

### **Mapping the restaurants across Richmond Town based on their cuisine**

## **Graph 1(a)**

```{r}
ggplot() +
  geom_sf(data = buildings, colour = "burlywood1") +
  geom_sf(data = roads, colour = "gray80") +
  geom_sf(
    data = restaurants %>% drop_na(cuisine),
    aes(fill = cuisine),
    colour = "White",
    shape = 21,
    size = 3
  ) +
  theme(legend.position = "right") +
  labs(title = "Restaurants in Richmond Town, Bangalore",
       caption = "Based on osmdata")
```
### **Analysis** 
This Graph represents various restaurants spread across Richmond Town in central Bangalore. The restaurants have been categorized based on their cuisine and color codded accordinlgy to provide a clearer visualisation and understanding. 

## **Graph 1(b)**

```{r using tmap}
tmap_mode("view") +
tm_shape(buildings) +
  tm_fill(col = "grey80") +

tm_shape(roads) +
  tm_lines(col = "gold") +

tm_shape(greenery) +
  tm_polygons(col = "yellow") +
  
tm_shape(parks) +
  tm_polygons(col = "orange") +

tm_shape(restaurants) +
  tm_dots(col = "purple")
```
### **Analysis**
This graph Represents Richmond Town in central Bangalore and the various elements embedded within this part of the city. Buildings, roads, greenery, parks, and restaurants that have made my childhood. These elements have been color codded to proivde a better visualizations and understanding. 

## **PART B** 

### **In part B we will be analysing and plotting all the villages and towns across India that have the word "pur" or "pura" in their names.**

### **Reading-in and cleaning-up the villages data set**

```{r}
villages <- read_csv("Data/Villages.csv")
villages
```

```{r}
villages$`NAME` %>% unique()
```

```{r}
villages <- villages %>% 
  drop_na(NAME) %>% 
  separate(col = NAME, into = c("NAME", NA, NA), sep = ";") %>% 
  separate(col = NAME, into = c("NAME", NA, NA), sep = ",")
```
```{r}
villages$NAME
```

```{r}
data("World")
india <- World %>% filter(iso_a3 == "IND")
crs_india <- st_crs(india)
points <- 
  data.frame(lon = rnorm(5, 77, 2),
             lat = rnorm(5, 23, 5))
str(points)
```

```{r}
points_sf <- st_as_sf(points,
         coords = c("lon", "lat"),
           crs = crs_india)
```


```{r}
ggplot() +
    geom_sf(data = india)
```
## **Graph 2(a)**

```{r}
data("World")
World
india <- World %>% filter(iso_a3 == "IND")
crs_india <- st_crs(india)
Villages_sf <- 
  

Villages_sf <- st_as_sf(villages,
         coords = c("LNG.", "LAT."),
           crs = crs_india)

ggplot() +
    geom_sf(data = india) +
    geom_sf(data = Villages_sf, colour = "purple", size = 2)

tmap_mode("view")
tm_shape(india)+ 
  tm_borders(col = "black", lwd = 1) +
  
  tm_shape(Villages_sf) + 
  tm_dots(col = "STATE", size = 0.5, legend.show = TRUE)
```
### **Analysis**
This Graph represents all the villages across India with the words 'pur' in their names. The villages have been categorised and color codded based on their states for a clearer visualization and understanding. As we can see through the graph, the state with the highest number of villages containing 'pur' in their names is karnataka while the state with the least number of villages containing 'pur' in their names are Nagaland and Assam. 

## **PART C** 

### **In Part C of this project, we will be working with a dataset termed 'BaldEagles', which is a tracking alliance project monitoring the migration of Bald Eagles in the Pacific Northwest.**

### **Reading-in and cleaning-up the Bald Ealges dataset.** 

```{r}
BaldEaglesPoints <- st_read ("Data/BaldEagles/points.shp")
BaldEaglesLines <- st_read ("Data/BaldEagles/lines.shp")
```

```{r}
data("World")
World
```

```{r}
Migration_countries <- World %>% filter(name %in%c("Canada","Alaska"))
Migration_countries
```

## **Graph 3(a)**

```{r}
tmap_mode("view") 
tm_tiles("Stamen.Watercolour") + 
  tm_shape(World) +
    tm_polygons("HPI")+

tm_shape(BaldEaglesLines) + 
  tm_lines(size = 0.1,
          col = "black") + 
  
  tm_shape(BaldEaglesPoints)+ 
  tm_dots(size = 0.1, 
          col = "white")
```
### **Analysis**
This Graph represents the migration of the great Bald Eagles across the countries of Alaska and Canada. 

### **Reflection** 

**These last few days have been treacherous, to say the least. As someone who has no experience coding, let alone a basic understanding of how computers work, this has been the most challenging course for me. On a more pleasant note, I truly enjoyed this challenge. In contrast to many students who picked up coding on the first day, I walked into the first day of class hesitant and lost. But I told myself, things take time, and you will learn with time.**

**What was really interesting to see was the transformation of a few codes into a whole graphic visualization. The ability of a computer to pick up on the smaller elements of life, such as trees, buildings, roads, and so on, and knit you a map of your childhood home is amusing. As dramatic as it may sound, it felt like I was watching my past come to life through a screen.**

**A concept that I’ve come to realise is the importance of embedding your art with a human essence, whether this essence triggers your senses, taste, smell, touch, or triggers a happy memory. Just as plotting my hometown in Rstudio with the use of different geometric aesthetics triggered a very happy childhood memory for me, I would want my art to do the same. Whether it’s amusement, sympathy, sorrow, or euphoria, the ability to invoke human emotions and knit experiences for all of us lies with us, and that’s a code I’d like to run for the rest of my life as an aspiring artist.**